Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw

For each combination of the intependent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. %ADD SHAKESPEARE

@@

\subsection*{Pelplexity of test set}

\subsection*{Perplexity of generated sentences}
Perplexity of generated sentences decreased with increased
\ngram length

>>>>

For each combination of the independent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. We did the same the Shakespeare corpus
but generated only 7 sentences for each treatment combination.

@@

\subsection*{Perplexity of test set}
For each corpus, perplexity of test set decreased when the models
were run for longer $n$-grams, and the perplexity
leveled off starting at $n=3$ (figure \ref{fig:test}). Probability computation type had no effect.

Smoothing slightly increased perplexity. The increase
was larger for larger $n$.

\begin{figure}
\begin{center}
<<echo=F,fig=T,height=9>>=
test.plot()
@
\end{center}
\caption{\label{fig:test}Perplexities of the test corpora by $n$-gram length and probability computation method for models trained on the respective training corpora.}
\end{figure}

\subsection*{Perplexity of generated sentences}
Perplexity of generated sentences decreased with when longer $n$-grams
were used in the model (figure \ref{fig:gen}). The perplexity
leveled off starting at $n=3$. Probability computation type did not
affect perplexity.
